\section{Introduction}
\vspace{-1mm}

Web is a major information portal on mobile devices~\cite{mobilestat}. However, web browsing is poorly optimized and continues to consume a
significant portion of battery power on mobile devices~\cite{thiagarajan2012killed,d2016energy,cao2017deconstructing}. Heterogeneous
multi-cores, such as the ARM big.LITTLE architecture~\cite{arm},  offer a new way for energy-efficient mobile computing. These platforms
integrate multiple processor cores on the same system, where each processor is tuned for a certain class of workloads to meet a variety of
user requirements. However, current mobile web browsers rely on the operating system to exploit the heterogeneous cores. Since the operating system has little
knowledge of the web workload and how does the network affect web rendering, the decision made by the operating system is often
sub-optimal. This leads to poor energy efficiency~\cite{zhu2015event}, draining the battery faster than necessary and irritating mobile
users. 

Rather than letting the operating system make all the scheduling decisions by passively observing the system's load, our work enables the
browser to actively participate in decision making. Specifically, we want the browser to decide which heterogeneous core and the optimum
processor frequencies to use to run the rendering engine. To effectively schedule the rendering process, the decisions must consider the
web content, the optimization goal, and how the network affects the rendering process. Instead of developing a hand-crafted approach that
requires expert insight into a specific computing and networking environment, we wish to develop an automatic technique that can be
portable across environments. We achieve this by employing machine learning to automatically build predictors based on empirical
observations gathered from a set of training web pages. The
trained models are then used at runtime by the web browser to predict the optimum processor configuration for any \emph{unseen} webpage. %Such an approach
%avoids the pitfalls of using a hard-wired heuristics that require human modification every time the optimization criterion or hardware
%changes.


The key contribution of this paper is a novel machine learning based web rendering scheduler that can leverage knowledge of the network and webpages to optimize mobile web browsing. 
We compare our approach against
two state-of-art web browser schedulers~\cite{YZhu13,ren2016optimise} on a representative ARM big.LITTLE mobile platform. Experimental results show that our approach outperforms the
state-of-the-arts by delivering over 1.2x (up to 1.4x) improvement across evaluation metrics.
Our techniques are generally applicable, as they are
useful for not only web browsers but also a large number of mobile apps that are underpinned by web rendering techniques~\cite{Charland}.
