\documentclass[journal]{IEEEtran}
\input{preamble}
\usepackage{multirow}

\begin{document}

\title{Network-Aware Mobile Web Browsing}


\author{
Jie Ren, Xiaomin Wang, Jianbin Fang, Yansong Feng, Feng Tian, Jie Zheng, Zheng Wang

 \thanks{J. Ren, X. Wang, F. Tian are with Shaanxi Normal University, China}%
 \thanks{J. Fang is with National University of Defense Technology, China}
 \thanks{Y. Feng is with Peking University, China}
 \thanks{J. Zheng is with Northwest University, China}
 \thanks{Z. Wang is with Lancaster University, UK}

}


%\author{
%
%\IEEEauthorblockN{Jie Ren\IEEEauthorrefmark{2}, Xiaoming Wang\IEEEauthorrefmark{2}, Jianbin Fang\IEEEauthorrefmark{4}, Yansong
%Feng\IEEEauthorrefmark{5}, Feng Tian\IEEEauthorrefmark{2}, Jie Zheng\IEEEauthorrefmark{3}, Zheng Wang\IEEEauthorrefmark{1}}
%
% \IEEEauthorblockA{
%\IEEEauthorrefmark{2} Shaanxi Normal University, China, \IEEEauthorrefmark{3}Northwest University, China \IEEEauthorrefmark{4}National
%University of Defense Technology, China, \IEEEauthorrefmark{5} Peking University, \IEEEauthorrefmark{1}Lancaster University }

%}
%\IEEEauthorrefmark{2}\{renjie, wangxm, tianfeng\}@snnu.edu.cn, \IEEEauthorrefmark{3}\{hwang, jzheng\}@nwu.edu.cn,
%\IEEEauthorrefmark{1}z.wang@lancaster.ac.uk}


% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
Web browsing is an important application domain, but it imposes a significant power burden on mobile devices. While the heterogeneous
multi-core design offers the potential for energy-efficient computing, existing web browsers and operating fail to exploit the hardware
to optimize mobile web browsing. Our work introduces a better way to optimize web browsing on heterogeneous mobile devices. We achieve
this by developing a machine learning based approach to predict which of the optimal processor setting for rendering the web content. We
do so by first learning, offline, a set of predictive models for a range of networking environments. We then choose a learnt model at
runtime to predict the optimal processor configuration. The prediction is based on the web content, the network status and the
optimization goal. We evaluate our approach by applying it to the Chromium browser and testing it on a representative big.LITTLE mobile
platform. We apply our approach to the top 1000 hottest websites across seven typical networking environments. Our approach achieves over
80\% of the performance delivered by a perfect predictor. We obtain, on average, over 20\% faster response time and 40\% more energy
reduction when compared to two state-of-the arts.
\end{abstract}





% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\input{intro}
\input{motivation}
\input{overview}
\input{modelling}
\input{results}
\input{related_work}
\input{conclusions}

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,refs}


% that's all folks
\end{document}
